StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-10 paper/paper.tex
Add oopsla07 and ics06 to related work

This approach is in contrast to the continuous query approach taken by many other streaming
systems.

@@

The Aurora system~\cite{Carney:2002:MSN:1287369.1287389} introduces the concept of
\emph{load shedding}, or compensating for
resource overload by comparing job specific quality of service metrics with target levels.
StreamReduce aims to incorporate load shedding to dynamically tune jobs in the face of
impending time and resource constraints.

@@

The most important piece Dyanmic Knobs offers to the DSMS space is dynamic
\emph{peak load provisioning}. Their system can adjust downward the amount of resources,
machines, etc. required for normal load and quickly adjust these levels back up to
handle load spikes. Combined with Aurora's load shedding, peak load provisioning can
be used to create a DSMS that uses less resources in both the normal and peak load
states.

@@

>>>>

This approach is in contrast to the continuous query approach taken by many other streaming
systems. StreamReduce uses this snapshot approach.

@@

The Aurora system~\cite{Carney:2002:MSN:1287369.1287389} introduces the concept of
\emph{load shedding}, or compensating for
resource overload by comparing job specific quality of service metrics with target levels and
dropping items from the data stream.
StreamReduce aims to incorporate load shedding to dynamically tune jobs in the face of
impending time and resource constraints. On the other hand, it may be the case that
parts of a processing pipeline struggle to provide enough data to keep the next stage busy.
In this case, a streaming system would like to implement
\emph{early phase termination}~\cite{Rinard:2007:UEP:1297027.1297055}, or preemptively kill
a stage in the pipeline that is not capable of keeping all workers busy.

@@

The most important piece Dynamic Knobs offers to the DSMS space is dynamic
\emph{peak load provisioning}. Their system can adjust downward the amount of resources,
machines, etc. required for normal load and quickly adjust these levels back up to
handle load spikes. Combined with Aurora's load shedding, peak load provisioning can
be used to create a DSMS that uses less resources in both the normal and peak load
states.

@@

The combination of load shedding, task killing and substitution transformations presents
an opportunity for the results of a computation performed by StreamReduce to be distorted.
Rinard~\cite{Rinard:2006:PAB:1183401.1183447} describes a method for bounding the distortion
introduced when discarding tasks. By breaking a computation into tasks, which in StreamReduce
consist of processing an individual datum at a worker, we can measure a
\emph{probabilistic distortion model} for a job, which gives bounds on its accuracy at different
task failure rates. I use this approach in the case study discussed in Section~\ref{sec:evaluation}.
